True versus apparent shapes of astrophysical bow shocks

### 2017-02-15 papers/Paper1/sec-conic.tex
Insert equations for \theta'_c and R'_90 and use of tilded variables

\begin{align}
R_{90} = b\left[\pm \left(1-\frac{x_0^2}{a^2}\right)\right]^{1/2}\label{eq:conic-R90}
\end{align}

Now, we can invert equations (\ref{eq:Rc-conic}) and (\ref{eq:conic-R90}) to estimate the parameters $a$ and $b$.
But first is useful to define the quantities $A \equiv \frac{R_c}{R_0}$ and $B\equiv \frac{R_{90}}{R_0}$ for simplification purposes.

\begin{align}
  \frac{a}{R_0} &= \frac{A}{\pm\left(2A-B^2\right)} \label{eq:a-con}\\
  \frac{b}{R_0} &= \frac{A}{\left|2A-B^2\right|^{1/2}} \label{eq:b-con}
\end{align}

@@

\begin{align}
\tan\theta_c = \frac{2A-B^2}{\left|2A-B^2\right|^{1/2}} \label{eq:th_c}
\end{align}

Note that the term $2A-B^2$ acts as a discriminant which determine the quadric we are working with.

@@

Defining  $f(i;\theta_c)\equiv\left(1\pm\tan^2\theta_c\tan^2i\right)^{1/2}$ we find that:
\begin{align}
\frac{R'_0}{D'}=\frac{R_0}{D}\left(1\pm A\cot^2\theta_c(f(i;\theta_c)-1) \right)
\label{eq:qprime}
\end{align}
%Where $A\equiv \frac{R_c}{R_0}$
The Radius of curvature in the observer's frame is given by $R'_c=\frac{b'^2}{a'}$. Then:
\begin{align}
A'\equiv  \frac{R'_c}{R'_0} = \frac{A}{\cos^2 i f(i;\theta_c)\frac{q'}{q}}
  \label{eq:Aprime}
\end{align}
where $q=\frac{R_0}{D}$ and $q' = \frac{R'_0}{D'}$. 
% \begin{figure*}
% \includegraphics[width=0.8\linewidth]{conic2}
% \label{fig:conic2}
% \caption{Graphic example of the increasing of the projected radius of curvature with inclination}
% \end{figure*}

>>>>

\begin{align}
R_{90} = \tan\theta_c\left[2aR_0\mp R_0^2\right]^{1/2}\label{eq:conic-R90}
\end{align}

Now, we can invert equations (\ref{eq:Rc-conic}) and (\ref{eq:conic-R90}) to estimate the parameters $a$ and $b$.
%But first is useful to define the quantities $\tilde{R}_c \equiv \frac{R_c}{R_0}$ and $\equiv \frac{\tilde{R}_{90}}{R_0}$ for simplification purposes.
Hereafter is useful to denote with a tilde quantities which are normalized with $R_0$:

\begin{align}
  \tilde{a}\equiv \frac{a}{R_0} &= \pm\frac{\tilde{R}_c}{\left(2\tilde{R}_c-\tilde{R}_{90}^2\right)} \label{eq:a-con}\\
  \tilde{b}\equiv \frac{b}{R_0} &= \frac{\tilde{R}_c}{\left|2\tilde{R}_c-\tilde{R}_{90}^2\right|^{1/2}} \label{eq:b-con}
\end{align}

@@

\begin{align}
\tan\theta_c = \pm \left|2\tilde{R}_c-\tilde{R}_{90}^2\right|^{1/2} \label{eq:th_c}
\end{align}

Note that the term $2\tilde{R}_c-\tilde{R}_{90}^2$ acts as a discriminant which determine the quadric we are working with.

@@

Defining  $f(i;\theta_c)\equiv\left(1\pm\tan^2\theta_c\tan^2i\right)^{1/2}$ we find that:
\begin{align}
\frac{R'_0}{D'}=\frac{R_0}{D}\left(1\pm \tilde{R}_c\cot^2\theta_c(f(i;\theta_c)-1) \right)
\label{eq:qprime}
\end{align}
%Where $A\equiv \frac{R_c}{R_0}$
The Radius of curvature in the observer's frame is given by $R'_c=\frac{b'^2}{a'}$. Then:
\begin{align}
  \tilde{R}_c'\equiv  \frac{R'_c}{R'_0} &= \frac{\tilde{R}_c}{\cos^2 i f(i;\theta_c)\frac{q'}{q}}
  \label{eq:Aprime}\\
  \tan\theta_c & = \frac{\tan\theta_c}{\cos i f(i;\theta_c)} \\
  \tilde{R}'_{90} &= \frac{\left[2\tilde{R}_cf(i;\theta_c) \mp \tan^2\theta_c\frac{q'}{q})\right]^{1/2}}{\cos i f(i;\theta_c)\frac{q'}{q}}
\end{align}
where $q=\frac{R_0}{D}$ and $q' = \frac{R'_0}{D'}$.

% \begin{figure*}
% \includegraphics[width=0.8\linewidth]{conic2}
% \label{fig:conic2}
% \caption{Graphic example of the increasing of the projected radius of curvature with inclination}
% \end{figure*}
